---
title: "STAT 385 Final Project"
author: ""
date: "Due by 12:00 PM noon CST on 05/14/2021"
output: html_document
---



Submit a final project proposal and a storyboard. See Chapter 1 of Knaflic's **Storytelling with Data** for ideas on creating a storyboard. The proposal should include the following information:

- the name and roles of all of the group members

- tentative title of the project

- the dataset

- summary of the intentions and goals of the project

- storyboard


```{r}
library(tidyverse)
library(ggplot2)
library(shiny)

ccso_bookings <- read.csv("https://uofi.box.com/shared/static/9elozjsg99bgcb7gb546wlfr3r2gc9b7.csv")

dat <- ccso_bookings %>% dplyr::select(RACE, MARITIAL.STATUS, SEX, CITY, Days.in.Jail) %>%
  rename(Race = RACE) %>%
  mutate(Race = as.factor(Race))  %>%
  rename(MaritalStatus = MARITIAL.STATUS) %>%
  mutate(MaritalStatus = as.factor(MaritalStatus)) %>%
  rename(Sex = SEX) %>%
  mutate(Sex = as.factor(Sex)) %>%
  rename(City = CITY) %>%
  mutate(City = as.factor(City))

# Define UI for application that draws a histogram
ui <- fluidPage(
  titlePanel("Length of Time Spent in Champaign County Jails by Various Demographics"),
  
  sidebarPanel(
    
    checkboxGroupInput("checkRace", 
      h3("Race"), choices = list("White" = "White", 
      "Hispanic" = "Hispanic", "White (Hispanic)" = "White (Hispanic)", "Black" = "Black", "Asian/Pacific Islander" = "Asian/Pacific Islander", "Native American" = "Native American", "Unknonwn" = "Unknown")),
    
    checkboxGroupInput("checkMarital", 
      h3("MaritalStatus"), choices = list("Married" =  "Married", "Single" = "Single", "Seperated" = "Separated", "Significant Other", "Divorced" = "Divorced", "Widowed" = "Widowed", "Unknown" = "Unknown")),
    
    checkboxGroupInput("checkSex", 
      h3("Sex"), choices = list("Female" =  "Female", "Male" = "Male")),
    
    checkboxGroupInput("checkCity", 
      h3("City"), choices = list("Champaign" =  "Champaign", "Urbana" = "Urbana")),
    width = 3
  ),
    
  mainPanel( 
    # Show a plot of the generated distribution
    plotOutput("Plot")
  )
)
# Define server logic required to draw a ggplot
server <- function(input, output) {
    output$Plot <- renderPlot({
        # generate bins based on input$bins from ui.R
        dat <- dat %>% 
          filter(Race %in% input$checkRace) %>%
          filter(MaritalStatus %in% input$checkMarital) %>%
          filter(Sex %in% input$checkSex) %>%
          filter(City %in% input$checkCity)
        ggplot(dat, aes(x = dat$Days.in.Jail)) + 
          geom_histogram() + 
          theme_minimal() + 
          labs(x="Length of Time in Jail (Days)")
  })
}
# Run the app
shinyApp(ui = ui, server = server,options = list(height = 600))
```



#### Continuing on

```{r}
# Define UI for application that draws a histogram
ui <- fluidPage(
    
  tabsetPanel(
    
    tabPanel("SliderInput",
    # Sidebar with a slider input for number of bins 
      sliderInput(inputId = "bins",
                        label = "Number of bins:",
                        min = 1,
                        max = 50,
                        value = 30)
   ),  #the comma is important
   
    tabPanel("HistogramOutput",
    # Show a plot of the generated distribution
      plotOutput("distPlot")
      )
  )
)
# Define server logic required to draw a histogram
server <- function(input, output) {
    output$distPlot <- renderPlot({
        # generate bins based on input$bins from ui.R
        x    <- faithful[, 2]
        bins <- seq(min(x), max(x), length.out = input$bins + 1)
        # draw the histogram with the specified number of bins
        hist(x, breaks = bins, col = 'darkgray', border = 'white')
  })
}
# Run the application 
shinyApp(ui = ui, server = server, options = list(height = 500))
```


```{r}
# Define UI for application that draws a histogram
ui <- fluidPage(
    
  navlistPanel(
    
    tabPanel("SliderInput",
    # Sidebar with a slider input for number of bins 
      sliderInput(inputId = "bins",
                        label = "Number of bins:",
                        min = 1,
                        max = 50,
                        value = 30)
   ),  #the comma is important
   
    tabPanel("HistogramOutput",
    # Show a plot of the generated distribution
      plotOutput("distPlot")
      )
  )
)
# Define server logic required to draw a histogram
server <- function(input, output) {
    output$distPlot <- renderPlot({
        # generate bins based on input$bins from ui.R
        x    <- faithful[, 2]
        bins <- seq(min(x), max(x), length.out = input$bins + 1)
        # draw the histogram with the specified number of bins
        hist(x, breaks = bins, col = 'darkgray', border = 'white')
  })
}
# Run the application 
shinyApp(ui = ui, server = server, options = list(height = 500))
```


```{r}
# Define UI for application that draws a histogram
ui <- #fluidPage( #we replace fluidPage with navbarPage
    
  navbarPage("A Simple App",
    
    tabPanel("Slider Input",
    # Sidebar with a slider input for number of bins 
      sliderInput(inputId = "bins",
                        label = "Number of bins:",
                        min = 1,
                        max = 50,
                        value = 30)
   ),  #the comma is important
   
    tabPanel("Histogram Output",
    # Show a plot of the generated distribution
      plotOutput("distPlot")
      )
)
# Define server logic required to draw a histogram
server <- function(input, output) {
    output$distPlot <- renderPlot({
        # generate bins based on input$bins from ui.R
        x    <- faithful[, 2]
        bins <- seq(min(x), max(x), length.out = input$bins + 1)
        # draw the histogram with the specified number of bins
        hist(x, breaks = bins, col = 'darkgray', border = 'white')
  })
}
# Run the application 
shinyApp(ui = ui, server = server, options = list(height = 500))
```


```{r}
# Define UI for application that draws a histogram
ui <- fluidPage( 
    
  sidebarLayout(
    
    sidebarPanel("Slider Input",
    # Sidebar with a slider input for number of bins 
      sliderInput(inputId = "bins",
                        label = "Number of bins:",
                        min = 1,
                        max = 50,
                        value = 30)
   ),  #the comma is important
   
    mainPanel("HistogramOutput",
    # Show a plot of the generated distribution
      plotOutput("distPlot")
      )
  )
)
# Define server logic required to draw a histogram
server <- function(input, output) {
    output$distPlot <- renderPlot({
        # generate bins based on input$bins from ui.R
        x    <- faithful[, 2]
        bins <- seq(min(x), max(x), length.out = input$bins + 1)
        # draw the histogram with the specified number of bins
        hist(x, breaks = bins, col = 'darkgray', border = 'white')
  })
}
# Run the application 
shinyApp(ui = ui, server = server, options = list(height = 500))
```
<<<<<<< Updated upstream

12345 34
=======
>>>>>>> Stashed changes
